`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-01-13 analysis/VOCC/4-vocc-biotic.Rmd
code for scrambling

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Arrowtooth Flounder" 
    immature: FALSE
    region: "both odd year surveys"
    #region: "West Coast Vancouver Island"
    covs: "-tv-depth-only"
---

@@

#### Set parameters
```{r }
species <- params$species
region <- params$region
covs <- params$covs
immature <- params$immature

@@

paste("species =", species)
paste("region =", region)
paste("covs =", covs)
```

@@

#### Get species-specific optimal values from mountain plots for most abundant year
```{r, include=FALSE}
if (immature) {
  age <- "immature"
  d_all <- readRDS(paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-imm-biomass-prior-FALSE.rds"
  )) %>% filter(year > 2007)
} else {
  age <- "mature"
  try({
    d_all <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-total-biomass-prior-FALSE.rds"
    )) %>% filter(year > 2007)
  })
  try({
    d_all <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-mature-biomass-prior-FALSE.rds"
    )) %>% filter(year > 2007)
  })
}

nd_all <- readRDS(paste0("data/predicted-DO-new.rds")) %>% select(X, Y, year, temp, do_est)
fishing <- readRDS("data/fishing-effort-grid.rds")

d_all <- left_join(d_all, nd_all, by = c("X", "Y", "year"))
d_all <- left_join(d_all, fishing, by = c("X", "Y", "year"))
d_all$log_effort[is.na(d_all$log_effort)] <- -2.3

glimpse(d_all)
#hist(d_all$log_effort)
```

@@

skip_time <- NULL
delta_t_step <- year_range
delta_t_total <- year_range
```

#### TRIM environment to range sampled
```{r}
# d <- d %>% filter(do_est > 0.23) %>% filter(do_est < 7.91) # full range
d <- d %>%
  filter(do_est > 0.28) %>%
  filter(do_est < 7.06) # 0.005 and 0.995
# d <- d %>% filter(temp > 2.61) %>% filter(temp < 14.31) # full range
d <- d %>%
  filter(temp > 3.07) %>%
  filter(temp < 11.3) # 0.005 and 0.995
```

@@

fish_t
```

@@

write.csv(vocc, file = paste0(
  "data/_new_biotic/", age,  "-biotic-vocc-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), "-trim10.csv"
))
```

>>>>

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Arrowtooth Flounder" 
    immature: FALSE
    region: "both odd year surveys"
    #region: "West Coast Haida Gwaii"
    #region: "West Coast Vancouver Island"
    covs: "-tv-depth-only"
    scrambled_years: FALSE
---

@@

#### Set parameters
```{r }
species <- params$species
region <- params$region
covs <- params$covs
immature <- params$immature
scrambled_years <- params$scrambled_years

@@

paste("species =", species)
paste("region =", region)
paste("covs =", covs)
paste("scrambled =", scrambled_years) 
```

@@

#### Get species-specific optimal values from mountain plots for most abundant year
```{r, include=FALSE}
if (immature) {
  age <- "immature"
  d_all <- readRDS(paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-imm-biomass-prior-FALSE.rds"
  )) %>% filter(year > 2007)
} else {
  age <- "mature"
  try({
    d_all <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-total-biomass-prior-FALSE.rds"
    )) %>% filter(year > 2007)
  })
  try({
    d_all <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-mature-biomass-prior-FALSE.rds"
    )) %>% filter(year > 2007)
  })
}
#hist(d_all$log_effort)
```

@@

skip_time <- NULL
delta_t_step <- year_range
delta_t_total <- year_range

glimpse (d)
if (scrambled_years) {
  d2 <- list()

  set.seed(9999) 
  # set.seed(12345)
  # set.seed(98765) 
  original_years <- unique(d$year)
  new_years <- sample(original_years)
  convert <- cbind(original_years,new_years)
  convert
  for (i in seq_len(length(original_years))) {
    old_year <- as.integer(convert[[i,1]])
    fake_year <- as.integer(convert[[i,2]])
    d2[[i]] <- filter(d, year == old_year) %>% 
      mutate(year = fake_year )
     # browser()
  }
  d <- do.call(rbind, d2)
}
```

#### TRIM environment to range sampled
```{r}
nd_all <- readRDS(paste0("data/predicted-DO-new.rds")) %>% select(X, Y, year, temp, do_est)
fishing <- readRDS("data/fishing-effort-grid.rds")
#fishing <- readRDS("data/fishing-effort-grid-6hr.rds")

d <- left_join(d, nd_all, by = c("X", "Y", "year"))
d <- left_join(d, fishing, by = c("X", "Y", "year"))
d$log_effort[is.na(d$log_effort)] <- -2.3

glimpse(d)

# d <- d %>% filter(do_est > 0.23) %>% filter(do_est < 7.91) # full range
d <- d %>%
  filter(do_est > 0.28) %>%
  filter(do_est < 7.06) # 0.005 and 0.995
# d <- d %>% filter(temp > 2.61) %>% filter(temp < 14.31) # full range
d <- d %>%
  filter(temp > 3.07) %>%
  filter(temp < 11.3) # 0.005 and 0.995
```

@@

fish_t

# fished <- gf %>%
#   select(x, y, fishing_trend, mean_effort) 
# saveRDS(fished, file = paste0("data/fishing-effort-trend-6hr-", ssid_string, ".rds"))
```

@@

write.csv(vocc, file = paste0(
  "data/_scrambled3/", age,  "-biotic-vocc-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), "-trim10.csv"
))
```
